\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{ifthen}
\usepackage{longtable}
\usepackage{tabu}
\usepackage{changepage}
\usepackage{enumitem}
\usepackage[
    %backend=biber,
    sorting=ydnt,
    style=nature,
    url=false,
    doi=true
]{biblatex}

% To load the sweet icons in the fontawesome and academicicons package is a massive hassle. If you compile with pdflatex, fontawesome doesn't work but academicicons does. If you compile with xelatex, the Font Awesome font isn't found. I think this can be fixed by modifying the latex fontawesome.sty file to point it directly at the ttf or otf font file you want to use, like this:

% \usepackage{fontspec}
% \defaultfontfeatures{Path = /usr/local/texlive/2013/texmf-dist/fonts/opentype/public/fontawesome/ }

% There is an easier alternative, give in https://tex.stackexchange.com/questions/132888/fontawesome-font-not-found: just add the lines

% \usepackage{fontspec}
% \defaultfontfeatures{Extension = .otf}

% so that xelatex somehow finds the correct font file. This requires adding the fontspec package to get the \defaultfontfeatures command. Disgusting bodge.


\usepackage{fontspec}
\defaultfontfeatures{Extension = .otf}
\usepackage{fontawesome}
\usepackage{academicons}
\usepackage[left=1cm,right=1cm,top=1cm,bottom=1cm]{geometry}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
    }
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% !TEX TS-program = lualatex

\DeclareFieldFormat[article]{title}{\textbf{#1}}
% \DeclareFieldFormat{labelnumberwidth}{}
% \setlength{\biblabelsep}{0pt}
\definecolor{darkblue}{HTML}{2052be}
\pagenumbering{gobble}
%%%%%%%%%%
% Configure column spacing
%%%%%%%%%%
\newcolumntype{t}{>{\hsize=0.5}}
\newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\bibliography{ref}

\newcommand{\coll}{1.2}
\newcommand{\colr}{8}

\newcommand{\ind}[1]{
    \begin{adjustwidth}{0.5cm}{0.5cm}
        #1
    \end{adjustwidth}
}

\newcommand{\indsp}{
    \phantom{\hspace{0.5cm}}
}

\renewcommand{\hline}{
    \vskip\medskipamount % or other desired dimension
    \leaders\vrule width \textwidth\vskip0.4pt % or other desired thickness
    \vskip\medskipamount % ditto
    \nointerlineskip
}

\newcommand{\minipagelr}[4]{
    \noindent
    \begin{minipage}[t]{#1\textwidth}
        \begin{flushleft}
            #3
        \end{flushleft}
    \end{minipage}\hfill
    \begin{minipage}[t]{#2\textwidth}
        \begin{flushright}
            #4
        \end{flushright}
    \end{minipage}
}


% \newcommand{\newsection}[1]{\vspace{0.5cm}{\noindent\large\textbf{#1}}\hline}
\newcommand{\bighref}[2]{\href{#1}{\color{darkblue}\LARGE{#2}}}

\newcommand{\iconlinks}{
    \bighref{https://www.linkedin.com/in/peytondm/}{\faLinkedinSquare \:}
    \bighref{https://github.com/peytondmurray}{\faGithubSquare \:}
    \bighref{https://scholar.google.com/citations?user=NXE8TDYAAAAJ\&hl=en}{\aiGoogleScholarSquare \;}
    \bighref{https://orcid.org/0000-0003-0389-0611}{\aiOrcidSquare \;}
    \bighref{https://researchgate.net/profile/Peyton_Murray}{\aiResearchGateSquare \;}
    \bighref{https://mendeley.com/profiles/peyton-murray}{\aiMendeleySquare \;}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\contact}{
    \vspace{-0.5cm}
    \begin{longtabu} to \textwidth{X[1,l] X[1,c] X[1,r]}
        Tel: +1 408 761 9078 & \href{https://peytondmurray.github.io}{peytondmurray.github.io} & \href{mailto:peynmurray@gmail.com}{peynmurray@gmail.com}
    \end{longtabu}
}

\newcommand{\header}[1]{
    {\LARGE\textbf{#1}} \hfill \iconlinks
    \hline
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\expvoltaiq}{
    \textbf{Voltaiq}, Berkeley, CA \hfill Oct 2019 $-$ Present \newline
    \indsp \emph{Software Engineer} \newline
    \vspace{-2\topsep}
    \begin{itemize}[leftmargin=1cm]
        \item Developed and deployed bespoke, modern, and production-quality data analysis and visualization tools to provide quantitative insight into battery performance for some of the world's largest battery manufacturers using Django (with Django REST Framework), Plotly.js, and React.
        \item Followed an agile development cycle, allowing for rapid iteration and delivery of custom software solutions.
    \end{itemize}
}

\newcommand{\exptampere}{
    \textbf{Computational Physics Laboratory, Tampere University}, Finland \hfill Jan 2019 $-$ Aug 2019 \newline
    \indsp \emph{Postdoctoral Researcher} \newline
    \indsp Advisor: Lasse Laurson \newline
    \vspace{-2\topsep}
    \begin{itemize}[leftmargin=1cm]
        \item Simulated nanoscale magnetic materials using a combination of open source software and in-house code (Go, CUDA, and Python). Numerical calculations of domain wall motion were compared to an analytic model \cite{Skaugen2019}.
        \item Leveraged GPUs deployed as part of the \href{https://www.csc.fi}{CSC's} Taito-GPU supercluster to enable massively parallelized simulations.
    \end{itemize}
}

\newcommand{\expucdavis}{
    \textbf{Department of Physics, University of California, Davis} \hfill 2012 $-$ 2018 \newline
    \indsp \emph{Graduate Student Researcher} \newline
    \indsp Advisor: Kai Liu \newline
    \vspace{-2\topsep}
    \begin{itemize}[leftmargin=1cm]
        \item Developed \href{https://github.com/peytondmurray/PyFORC}{PyFORC}, a suite of open source tools for analyzing and visualizing magnetic measurements using the First-Order Reversal-Curves (FORC) technique (Python).
        \item Streamlined the Liu group's material analysis pipeline by developing \href{https://github.com/peytondmurray/tarmac}{tarmac}, a Python library for quickly visualizing Markov-chain monte carlo (MCMC) samples. This library makes it simple to identify correlations between parameters in a statistical model, and to evaluate convergence during curve fitting.
        \item Fabricated and characterized a wide range of nanoscale magnetic materials, including nanoparticles, thin films, single crystals, and patterned nanostructures using a variety of cutting-edge techniques. Programmed data acquisition and instrument control software for crucial laboratory equipment.
    \end{itemize}
}

\newcommand{\explbl}{
    \textbf{Physics Division, Lawrence Berkeley National Laboratory}, Berkeley, CA \hfill 2011 $-$ 2012 \newline
    \indsp \emph{Junior Specialist}, \href{https://atlas.cern/}{ATLAS Experiment} \newline
    \indsp Principal Investigator: Maurice Garcia-Sciveres \newline
    \vspace{-2\topsep}
    \begin{itemize}[leftmargin=1cm]
        \item Tested prototype next-generation hardware developed for tracking the trajectories of charged particles at the \href{https://home.cern/science/accelerators/large-hadron-collider}{Large Hadron Collider} (LHC), the largest particle physics experiment in the world.
        \item Developed system control GUI and backend for an integrated circuit tester (C++ and Qt; version control with SVN). These tools allowed for automated testing of hundreds of chips (entire wafers) at a time, greatly increasing throughput. Chips which passed tests \href{https://atlas.cern/updates/atlas-news/new-sub-detector-atlas}{were installed} as part of the Insertable B-Layer system at the LHC in 2014, enabling continued studies of the Higgs boson \cite{Collaboration2012}.
    \end{itemize}
}

\newcommand{\expalfalfa}{
    \textbf{Physics Department, Saint Mary's College of California}, Moraga \hfill 2010 $-$ 2011 \newline
    \indsp \emph{Research Assistant}, \href{http://egg.astro.cornell.edu/index.php/}{ALFALFA Collaboration} \newline
    \indsp Advisor: Ron Olowin \newline
    \vspace{-2\topsep}
    \begin{itemize}[leftmargin=1cm]
        \item Classified galactic and extragalactic astronomical observations as part of the Arecibo Legacy Fast-ALFA (ALFALFA) project, an international collaboration of astronomers based at the \href{https://naic.edu/ao/landing}{Arecibo Radio Observatory} in Puerto Rico.
    \end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document start
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\nocite{*}
\header{Peyton D. Murray}
\contact

\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Education} & University of California, Davis \hfill 2012 $-$ 2018 \newline
    \indsp {Ph. D. Physics: Dec 2018} \newline
    \indsp {M. S. Physics: Dec 2013} \\
    & \\
    & Saint Mary's College of California, Moraga \hfill 2007 $-$ 2011 \newline
    \indsp {B. S. Physics, Minor: Mathematics, \emph{summa cum laude} (GPA: 3.873)}
\end{longtabu}

\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Computing} & Python (proficient), C++ (intermediate), Go (intermediate), Javascript (intermediate), CUDA (intermediate)
\end{longtabu}

\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Technologies} & Git, Python scientific/data vis stack (scipy [contributor], numpy, matplotlib, cython, ...), pytest. Web development with Django (and Django REST), React+Redux, Jest, AngularJS. Jenkins and CircleCI for testing and deployment, codecov for test coverage.
\end{longtabu}

\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Skills} & Agile Development, Automated Testing, Simulations, Data Analysis, Statistics, Visualization, Linux, Python Data \& Visualization Ecosystem (numpy, scipy, pandas, dask, matplotlib, ...), Regression, Bayesian parameter estimation, HPC, Distributed Computing, VTK, Jekyll.
\end{longtabu}

\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Research \newline\& Experience} & \expvoltaiq \\
    & \exptampere \\
    & \expucdavis \\
    & \explbl \\
    & \expalfalfa
\end{longtabu}

\vspace{-0.8cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Teaching} & \emph{Teaching Assistant}, \textbf{Dept. of Physics, University of California, Davis} \hfill 2012 $-$ 2016 \\
    & \emph{Student Tutor and Live-In Mentor}, \textbf{Physics Dept., St. Mary's College of California} \hfill 2010 $-$ 2011
\end{longtabu}

\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Laboratory Skills} & \emph{Fabrication} \newline
    \vspace{-3mm}
    \ind{Sputtering, e-beam evaporation, and e-beam-/photo-lithography and lift-off.} \\
    & \emph{Magnetic Characterization} \newline
    \vspace{-3mm}
    \ind{Vibrating sample magnetometry (VSM), magneto-optic Kerr effect (MOKE), SQUID magnetometry, and magnetoresistance.} \\
    & \emph{Other Techniques} \newline
    \vspace{-3mm}
    \ind{X-ray diffraction (XRD), reciprocal space mapping (RSM), scanning electron microscopy (SEM), polarized neutron reflectometry (PNR), x-ray absorption spectroscopy (XAS) and magnetic circular dichroism (XMCD), and Hall effect and van der Pauw resistivity methods.}
\end{longtabu}

\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Publications} & \vspace{-0.55cm}\printbibliography[heading=none]
\end{longtabu}
\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Selected \newline Conferences} & P. D. Murray. \textbf{Invited colloquium:} \emph{Tuning Ionic Distributions for Multifunctional Materials}. Tampere University, Tampere, Finland (2019). \newline

    P. D. Murray, D. A. Gilbert, A. J. Grutter, B. J. Kirby, D. Hernandez-Maldonado, M. Varela, Z. E. Brubaker, R. V. Chopdekar, V. Taufour, R. Zieve, J. R. Jeffries, E. Arenholz, Y. Takamura, J. Borchers, and K. Liu. \textbf{Poster:} \emph{Interfacial-Redox-Induced Tuning of Superconductivity in YBa$_2$Cu$_3$O$_{7-\delta}$}. International Conference on Magnetism and Magnetic Materials, San Francisco, CA (2018). \newline

    P. D. Murray, Z. Chen, D. A. Gilbert, J. Zang, T. Stückler, K. Lenz, B. B. Maranville J. Fassbender, H. Yu, J. Borchers, and K. Liu. \textbf{Poster:} \emph{Topological Hall Effect in Planar Artificial Skyrmion Lattices}. Conference on Magnetism and Magnetic Materials, Pittsburgh, PA (2017). \newline

    P. D. Murray, D. A. Gilbert, A. J. Grutter, A. L. Ionin, R. V. Chopdekar, A. T. N’Diaye, B. J. Kirby, B. B. Maranville, Y. Takamura, E. Arenholz, K. Liu, and J. Borchers. \textbf{Talk:} \emph{Complete Suppression of Magnetism in Gd/(La,Sr)CoO$_3$ Films via Redox Design of Oxygen Distributions}. Conference on Magnetism and Magnetic Materials, New Orleans, LA (2016). \newline
\end{longtabu}
\vspace{-0.5cm}
\begin{longtabu} to \textwidth{X[\coll] X[\colr]}
    \textbf{Awards} & 3rd Place Winner, 2020 John D. Hunter Excellence in Plotting Contest. \href{https://www.youtube.com/watch?v=cBPwU2T46vw}{Entry (video)}, \href{https://github.com/peytondmurray/jdh2020}{Source repository}
\end{longtabu}

\end{document}
